\documentclass[project,12pt,lof]{CSUNthesis}

%% BEGIN Font Selection
\usepackage{tgtermes}
%% END Font Selection

\usepackage{subfiles}

\title{Linux-Based Automotive Audio System}

\author{Jordan Yelloz}
\contact{jordan.yelloz@my.csun.edu}

\committee{Dr. Jeffrey Wiegley}
          {Yevgeniya Mushkatblat}
          {Dr. John Noga}

\coordinator{Richard O. Sight, Ph.D}

\submitted{ }{ }

\setlength{\baselineskip}{24pt}

\references{thesis}{thesis}

\abstract{
	\paragraph{ }
In recent years, the amount of personal electronic devices has greatly increased.
With a host of different manufacturers and standards, there has been a difficulty to properly integrate these devices.
An product category which suffers noticeably from this shortcoming is the automotive field.
While car companies and consumer electronics companies have been making progress recently and introducing new products to the market, their solutions are suboptimal for many consumers.
High cost, lack of features, and lack of customizability are all issues that diminish the efforts of the industry making these devices.
This paper mentions some existing products and describes their inadequacies.
The solution to this problem is a new platform based on the latest advances free software and commodity hardware.
The final product includes a set of software with a graphical user interface capable of displaying necessary information as well as a reference hardware platform from which custom purpose-fit hardware can be built.
This computer will be able to connect directly to the amplifier and electrical power supply of an automobile to operate as expected inside the car.
The result should be a reasonably-priced solution for knowlegeable users who want a simplified, but customizable solution for their automotive audio needs.
}

\usepackage[pdftex,
			debug=true,
			implicit=false,
			pdfstartview=FitH,
			colorlinks=false,
			bookmarks=true,
			naturalnames=true,
			plainpages=false,
			breaklinks=true,
			final=true,
			draft=false,
			pdfauthor={Jordan Yelloz},
			pdftitle={Linux-Based Automotive Audio System}]
			{hyperref}
\begin{document}

\setlength{\baselineskip}{24pt}

\chapter{Introduction}

\subfile{chapter1/introduction}

\chapter{Related Works}

\subfile{chapter2/related-works}

\chapter{My Solution}

\chapter{Conclusion and Further Research}

\subfile{chapter4/conclusion}

\chapter*{References}

\references{}

\end{document}
