In 2007, at the start of this project, there were few options for advanced automotive audio systems.
In 2016 there are several options to choose from and large commercial entities have deployed their software in new cars.
It is also possible to purchase full-featured hardware running advanced operating systems such as Android and install them into any compatible automotive dashboard.

\section{Complete Solutions}

There are a few existing solutions to the problem described in this project.
They are fairly new and some are backed by large entities as well as small independent developers.

\subsection{Harman Connected Car}

\paragraph{}
Harman Connected Car <<harman-connected-car>> is a large software project claiming to support bringing a wide range of automotive subsystems within a multimedia environment.
This project appears to an extensive and professional solution and is currently deployed or being deployed in automobiles of at least 24 major international car brands <<harman-connected-vehicles>>.
Features such as audio, communications, air conditioning integration, navigation, voice recognition, cameras, and sensors are supported.
Furthermore, the solution also includes a remote management platform to handle over-the-air software updates.

\subsection{iCarus}

\paragraph{}
The iCarus Car PC <<icarus>> is a commercially available independent  hardware and software solution that can be inserted into a car dashboard and used for similar purposes as this project.
The software runs Linux with some proprietary application code.
The hardware consists of a custom board with several peripherals such as 802.11 and Bluetooth wireless networking connected to an off-the-shelf Raspberry Pi single-board PC.
At the time of this writing, a fully functioning unit can be purchased directly from the maker for 284 EUR <<icarus-shop>>.

\subsection{Wind River Helix Chassis}

\paragraph{}
Helix Chassis <<helix-chassis>>, by Wind River, is another full software solution by a major technology company.
It offers a similar set of capabilities as the Harman Connected Car solution.
Wind River claims over 70 customers implementing solutions with the Helix Chassis suite.
A sub-project of the Helix Chassis suite, Cockpit offers a Linux-based platform based on the to-be-mentioned GENIVI framework with a custom JavaScript-based user interface and application system.

\section{Frameworks and Standards}

\paragraph{}
There are also efforts to provide open standards as well as a base platform for automotive information and audio systems.

\subsection{Android and Android Auto}

\paragraph{}
Android is a Linux-based operating system targeted toward mobile and entertainment devices such as phones, tablets, and television set top boxes.
It is possible for independent developers to leverage the Android Open Source Project in building a custom operating system for automotive systems on top of existing Android components.
Android has also released its own automotive variant, Android Auto, which is deployed in several 2016 and 2017 car dashboards as well as available in Android phones docked inside a car.
Application development in Android is typically carried out with Java or other languages compatible with the Java Virtual Machine.

\subsection{GENIVI}

\paragraph{}
GENIVI is an alliance of several automotive manufacturers and automotive audio suppliers coordinating on several open source components to provide the core functionalities necessary to provide the foundation of a custom automotive operating system <<genivi-about>>.

\subsection{Freesmartphone.org}

\paragraph{}
Freesmartphone.org is an open source project to provide a similar set of middleware interfaces and implementations for independent development of fully user-customizable mobile phones and tablet devices <<fso-home>>.
While this project is not focused on automotive audio, many of its concerns are shared with an automotive audio project.
