\paragraph{}
Given the wide-ranging solutions provided by some of the newer commercially backed systems that are shipping in newer automobiles as well as the dominance of the Android operating system for mobile devices, this project would need a significant amount of work to be performed to achieve competitive market share, though that was not a goal of this project.
This section outlines several future areas which this project could be expanded in scope and depth.
One area this project should not receive any development is any "Cloud" integration.

\section{Automotive Integration}

\paragraph{}
A clear area of functionality that could benefit this project is the addition of features that integrate with automotive hardware such as On-Board Diagnostics (OBD), Tire Pressure Monitoring System (TPMS), and climate control.

\section{Navigation}

\paragraph{}
While this project can supply maps and geolocation, it does not supply any navigation directions from one location to another.
Many existing solutions provide navigation instructions and traffic integration.

\section{Mesh Networking}

\paragraph{}
An ambitious, largely untapped, and potentially dangerous power of every car on the road containing wireless networking capabilities introduces many possibilities for the future of transportation.
For example, automobiles could potentially broadcast important information to each other in order to inform drivers of upcoming hazards and other conditions such as average speed.
This type of network can provide a non-commercial, peer-to-peer replacement of proprietary live traffic data offered by paid services.

\section{Security}

\paragraph{}
This project, as-is, does not suffer from many security threats since there is not much at stake, a limited surface to attack, and no valuable information stored.
However, any networking features and integration with automotive components will most likely place a system such as this project under a much larger threat.
